Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-12-08 doc/JFLA2022/Slides/Slides.tex
initial slides

@@

\usepackage{texments}
%%% for movies by alectryon
\usepackage{./movies/snippets/assets/alectryon}
\usepackage{./movies/snippets/assets/pygments}

@@

\newcommand{\pathtomovies}{./movies}

\newcommand{\inputsnippets}[1]
  {{\setlength{\itemsep}{1pt}\setlength{\parsep}{0pt}% Adjust spacing
    \alectryon@copymacros\begin{io}
      \forcsvlist{\item\@inputsnippet}{#1}
    \end{io}}}
\let\input@old\input % Save definition of \input
\newcommand{\@inputsnippet}[1]
  {{\renewenvironment{alectryon}{}{}% Skip \begin{alectryon} included in snippet
    \input@old{{\pathtomovies}/snippets/#1}}}
\makeatother

% End of Alectryon stuff
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Lexicographic exponentiation: An example of proof documentation with Alectryon}

\author{Labri Coq working group}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \maketitle
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Introduction}
  \begin{block}{}
We show a small but non-trivial example of using Alectryon
for writing a documentation (in pdf) of a proof written in Coq.    
  \end{block}

>>>>

\definecolor{plugincolor}{rgb}{0.0,0.0,0.0}
\definecolor{mathcolor}{rgb}{1.0,0.3,0.0}
\definecolor{coqstylecolor}{rgb}{0.0,0.0,01.0}

\definecolor{metavarcolor}{rgb}{0.5,0.0,1.0}
\definecolor{darkgreen}{rgb}{0.1,0.7,0.1}
\definecolor{answercolor}{rgb}{.08,.15,.8}
\definecolor{normalcolor}{rgb}{0.0,0.0,0.0}
\definecolor{exbluecolor}{rgb}{0.1,0.1,0.9}
\definecolor{dontlookcolor}{rgb}{0.5,0.5,0.5}
\definecolor{termcolor}{rgb}{0.0,0.1,0.9}
\definecolor{lookcolor}{rgb}{0.9,0.1,0.0}
\definecolor{prooftermcolor}{rgb}{0.3,0.1,1.0}
\definecolor{typecolor}{rgb}{1.0,0.6,0.0}
\definecolor{taccolor}{rgb}{0.70,0.10,0.0}
\definecolor{pink}{rgb}{0.8,0.6,0.6}
\definecolor{darkmagenta}{rgb}{0.4,0.0,0.6}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}

@@

\usepackage{texments}
%%% for movies by alectryon
\usepackage{./alectryon}
\usepackage{../pygments}

@@

\newcommand{\pathtomovies}{..}%/movies}

\newcommand{\inputsnippets}[1]
  {{\setlength{\itemsep}{1pt}\setlength{\parsep}{0pt}% Adjust spacing
    \alectryon@copymacros\begin{io}
      \forcsvlist{\item\@inputsnippet}{#1}
    \end{io}}}
\let\input@old\input % Save definition of \input
\newcommand{\@inputsnippet}[1]
  {{\renewenvironment{alectryon}{}{}% Skip \begin{alectryon} included in snippet
    \input@old{{\pathtomovies}/#1}}}
\makeatother

% End of Alectryon stuff
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Hydras \& Co.: Formalized mathematics in Coq\\
 for inspiration and entertainment
}
\date{JFLA, February 2022}
\author{
Pierre Castéran %\inst{1}
\and
    Jérémy Damour %\inst{2}
\and
Karl Palmskog %\inst{3}
\and Clément Pit-Claudel %\inst{4}
\and Théo Zimmermann %\inst{5}
}

% \institute{
% Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France  %\\
%  % \email{pierre.casteran@labri.fr}
% \and
% Univ. de Paris, F-75013 Paris, France
% \and
% KTH Royal Institute of Technology, Stockholm, Sweden
% \and
% MIT CSAIL, Cambridge, Massachusetts, USA
% \and
% Inria, Univ. de Paris, CNRS, IRIF, UMR 8243, F-75013 Paris, France
% }

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \maketitle
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Coq-community}
  \begin{block}{Objectives}
    \begin{itemize}
    \item
    \item
      \item Documentation on libraries
    \end{itemize}
  \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{What hydras are talking about?}
  \begin{block}{Hydra battles}
    \begin{itemize}
\item  \textcolor{mathcolor}{ordinals},
    \textcolor{mathcolor}{rapidly growing functions},
    \textcolor{mathcolor}{primitive recursive functions}, etc.
    \item \textcolor{coqstylecolor}{dependently typed functions},
      \textcolor{coqstylecolor}{proofs of well-foundedness},
         \textcolor{coqstylecolor}{impossibility proofs},
    \textcolor{coqstylecolor}{uniqueness of identity proofs (UIP)},
      \textcolor{coqstylecolor}{indefinite description (Hilbert's epsilon operator)},
    etc.
    \item \textcolor{plugincolor}{ackermann (Russel O'Connor)},
      \textcolor{plugincolor}{gaia (Jos\'e Grimm)},
    \end{itemize}

  \end{block}

  \begin{block}{Addition chains}
    \begin{itemize}
    \item    \textcolor{mathcolor}{algorithmics},
       \textcolor{mathcolor}{arithmetic},
  \item 
    \textcolor{coqstylecolor}{monadic notations},
    \textcolor{coqstylecolor}{PHOAS},
  \textcolor{coqstylecolor}{parametricity}, etc.
    \item
      \textcolor{plugincolor}{paramcoq (Chantal Keller, Marc Lasson)} 
          \end{itemize}
  \end{block}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
  \frametitle{Tests with Beamer(1)}
  \begin{footnotesize}
      \inputsnippets{Schutte_Ex42a}   
      \inputsnippets{Schutte_Ex42b, Schutte_Ex42c}   
    \end{footnotesize}
\end{frame}
  \begin{frame}[fragile]
    \frametitle{Tests with Beamer(2)}

  \begin{footnotesize}
  \inputsnippets{Schutte_Ex42d, Schutte_Ex42e}   
  \end{footnotesize}

\end{frame}
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Introduction}
  \begin{block}{}
We show a small but non-trivial example of using Alectryon
for writing a documentation (in pdf) of a proof written in Coq.    
  \end{block}
